Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-24 Report/convergence_centralized.tex
before Nam's correction

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using this unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

>>>>

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each \ac{AO} step.
Using this unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

### 2015-11-24 Report/mse_formulation.tex
before Nam's correction

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receivers. The optimization subproblem to find transmit precoders for fixed \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
For fixed receivers, transmit precoders are obtained by solving \eqref{eqn-mse-2} iteratively by updating \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} found in previous iteration until termination as discussed in Section \ref{sec-3.2.1}.

>>>>

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receivers. The optimization subproblem to find transmit precoders for fixed \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
For fixed receivers, transmit precoders are obtained by solving \eqref{eqn-mse-2} iteratively by updating \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} found in previous step until termination as in Section \ref{sec-3.2.1} and Algorithm \ref{algo-1}.
